Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-22 awipev-CO2.Rmd
variable names modification according to part : traitement des variables 2

discrete_no_na$phcalc<- carb$pH
discrete_no_na$pco2calc<- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc<- NA
discrete_is_na$pco2calc<- NA
discrete <- rbind(discrete_no_na, discrete_is_na)
discrete <-discrete%>%dplyr::arrange(datetime)
```

@@

# pCO2
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb)

@@

            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "sal_fb") %>%

@@

      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%

@@

      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%

@@

      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%

@@

      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "T") %>%

@@

pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)

@@

    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2calc , nperm = 99)

pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, units="cm")
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="<i>p</i>CO<sub>2</sub>", ylab="<i>p</i>CO<sub>2</sub>") %>%
  dySeries("pco2_corr", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%

@@

# #plot for POSTER june 2019
# #plot of pCO2
# 
# #  add pCO2 atmospheric data from URL
# 
# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
# 
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
#            "Calculated from AT/CT"
# 
#           )
# 
# col <- c("blue","black","red")
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
#   scale_shape_discrete(labels=lab, guide="none")+
#   scale_colour_manual(labels=lab, values=col)+
#   labs(x = "", y ="", title = "") +
#   theme_bw() +
#   scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position="top",  #c(0.18, 0.85)
#                      legend.text=element_text(size=14, colour="black"),
#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank()
#                      )
# print(poster_pco2)
#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

>>>>

discrete_no_na$phcalc<- carb$pH
discrete_no_na$pco2_calc<- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc<- NA
discrete_is_na$pco2_calc<- NA
discrete <- rbind(discrete_no_na, discrete_is_na)
discrete <-discrete%>%dplyr::arrange(datetime)
```

@@

# pCO2
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

sal_xts <- dplyr::select(d_all, datetime, sal_fb)

@@

@@

      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "sal_insitu_ctd") %>%

@@

      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "temp_fb") %>%

@@

      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "temp_insitu_11m") %>%

@@

      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "temp_insitu_ctd") %>%

@@

pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)

@@

    dySeries("pco2_calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc , nperm = 99)

pco2_calc_pco2_corr_text <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2_calc_pco2_corr_text)
ggsave(paste0("figures/pco2_calc_pco2_corr.png"), pco2_calc_pco2_corr_text, units="cm")
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="<i>p</i>CO<sub>2</sub>", ylab="<i>p</i>CO<sub>2</sub>") %>%
  dySeries("pco2_corr", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
    dySeries("pco2_calc", label="pco2_calc",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%

@@

# #plot for POSTER june 2019
# #plot of pCO2
# 
# #  add pCO2 atmospheric data from URL
# 
# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
# 
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
#            "Calculated from AT/CT"
# 
#           )
# 
# col <- c("blue","black","red")
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2_calc, shape="lab" , color= "red"))+
#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
#   scale_shape_discrete(labels=lab, guide="none")+
#   scale_colour_manual(labels=lab, values=col)+
#   labs(x = "", y ="", title = "") +
#   theme_bw() +
#   scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position="top",  #c(0.18, 0.85)
#                      legend.text=element_text(size=14, colour="black"),
#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank()
#                      )
# print(poster_pco2)
#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
